Modeling Human Interactions in Collaborative Interactive Evolutionary Computation

### 2017-02-06 2017-GECCO-Modeling-User-Interactions-in-IEC/paper-body.tex
Finished revision.
Now we have 9 pages, but the problem is that once we add addresses and publishers to bibliography is going to be even more. We could eliminate the "unplugged" section of the paper that has nothing to do with the rest.

Table \ref{tab:urls} shows the total number of volunteers, nodes and edges 
in the graph after each experiment. Moreover, the total number of evaluated 
phenotypes for each volunteer is presented in figure 
\ref{fig:top-ranked-participation} where users are ranked by the 
number of phenotypes they rated. In the \emph{x} axis is the rank and in the \emph{y} axis 
the number of phenotypes evaluated using a logarithmic scale. Results show that when 
considering deployments B and G, the difference came with users with a medium level of participation.
When comparing all the experiments the deployment GG had the higher number of participation in users of all levels.

@@

Moreover, modeling the performance of an C-IEC system
involves understanding its dynamics. Previous works on browser-based
volunteer computing have used basic metrics such as: 
the number of users or the time spent by every one in the
computation \cite{DBLP:journals/gpem/LaredoBGVAGF14, 2016arXiv160101607M}. 
While works on other platforms such as SETI@home
\cite{javadi2009mining} have found that the Weibull, log-normal, and
Gamma distributions where viable modeles of the  
the availability of computing resources in several clusters.
This is in concordance with the results obtained in \cite{agajaj}, and also
browser-based volunteer evolutionary systems like NodIO \cite{DBLP:conf/gecco/MereloCGCRV16}.
The shape of those distributions is a skewed bell
with more resources in the {\em low} areas than in the high areas; i.e., 
there are many users that give a small amount of cycles, while there
are just a few that give many cycles.

In order to assess if C-IEC follows the same pattern, even when
using gamification techniques, participation was fittted to a 
Weibull distribution. Results in Figure \ref{fig:w2} and Figure \ref{fig:w3}
show that the same pattern appears in this case study.

\begin{figure}[!t]
    \centering
        \includegraphics[width=3.5in]{img/weibull_2.png}
    \caption{Experiment G. Weibull Fit}
    \label{fig:w2}
\end{figure}
\begin{figure}[!t]
    \centering
        \includegraphics[width=3.5in]{img/weibull_3.png}
    \caption{Experiment GG. Weibull Fit}
    \label{fig:w3}
\end{figure}

@@

In this instalation the components of the framework used where EvoSpace and the EA.
Information from users was limited to a stream of readings from the sensor.

@@

\begin{figure}[!t]
    \centering
        \includegraphics[width=3.5in]{img/interfaceXYZ.png}
    \caption{User interface of the XYZ application, used by artists to select the best pair of the current generation.}
    \label{fig:xyz}
\end{figure}

@@

Volunteer-based and C-IEC systems involve the dynamic 
interaction of many entities and artifacts. Employing a human-centered approach 
can benefit researchers to understand and visualize this kind of systems better.
In this paper a human-centered software framework was proposed, and was validated
through the implementaion and refinement of three C-IEC applications.
This framework enabled the implementation of a gamification technique 
to improve engagement in a case study. Providing a common arena where users are aware of the
activities of other users in the social vicinity. Following a hybrid data model approach
gives developers and project owners options when innovating with other means
of interaction or new applications.

@@

Another line of work would be to study the negative effects of using 
gamification techniques to improve engagement, like cheating or competition.
Finally, the refinement of the proposed Human-Centered framework will need
more case studies and further multi-disciplinary research.

\begin{acks}
  Reserved\\
  Space\\
  for\\
  Acks

>>>>

Table \ref{tab:urls} shows the total number of volunteers, nodes and edges 
in the graph after each experiment. Moreover, the total number of evaluated 
phenotypes for each volunteer is presented in figure 
\ref{fig:top-ranked-participation} where users are ranked by the 
number of phenotypes they rated. In the \emph{x} axis is the rank and in the \emph{y} axis 
the number of phenotypes evaluated using a logarithmic scale. Results show that when 
considering deployments B and G, the difference came with users with a medium level of participation.
When comparing all the experiments the deployment GG had the higher
number of participation in users of all levels, besides attracting a
bigger number of users.

@@

Moreover, modeling the performance of an C-IEC system
involves understanding its dynamics. Previous works on browser-based
volunteer computing have used basic metrics such as
the number of users or the time spent by every one in the
computation \cite{DBLP:journals/gpem/LaredoBGVAGF14, 2016arXiv160101607M}. 
While works on other platforms such as SETI@home
\cite{javadi2009mining} have found that the Weibull, log-normal, and
Gamma distributions where viable modeles of the  
the availability of computing resources in several clusters, which  is in concordance with the results obtained in \cite{agajaj}, and also
browser-based volunteer evolutionary systems like NodIO \cite{DBLP:conf/gecco/MereloCGCRV16}.
The shape of those distributions is a skewed bell
with more resources in the {\em low} areas than in the high areas; i.e., 
there are many users that give a small amount of cycles, while there
are just a few that give many cycles. In order to assess gamification techniques alongside C-IEC follows the
same pattern, participation was fittted to a 
Weibull distribution,
 and shown in Figures \ref{fig:w2} and \ref{fig:w3}, confirming  this model for user interaction, although with different fitted
values in each case. 
%
\begin{figure}[!t]
    \centering
        \includegraphics[width=3.5in]{img/weibull_2.png}
    \caption{Experiment G. Weibull Fit}
    \label{fig:w2}
\end{figure}
%
\begin{figure}[!t]
    \centering
        \includegraphics[width=3.5in]{img/weibull_3.png}
    \caption{Experiment GG. Weibull Fit}
    \label{fig:w3}
\end{figure}

@@

In this instalation the components of the framework used where EvoSpace and the EA.
Information from users was limited to a stream of readings from the
sensor.
% This has nothing to do with the rest of the paper. You are not
% modeling anything. It's just another application of the
% framework. Could be mentioned in the state of the art, that's
% all. We should devote more space to the study of user interactions.

@@

\begin{figure}[!t]
    \centering
        \includegraphics[width=3.5in]{img/interfaceXYZ.png}
    \caption{User interface of the XYZ application, used by artists to select the best pair of the current generation.}
    \label{fig:xyz}
\end{figure}
% Once again, no model, no relation to the rest of the paper. Either
% you talk about a model of interactions with humans and their
% similarity with the first case study, or you eliminate it. How do
% you tackle boredom? How do you increase engagement? Those are the
% paper's topics, you can't just drop it here because it's interactive
% - JJ

@@

Volunteer-based and C-IEC systems involve the dynamic 
interaction of many entities and artifacts. Employing a human-centered approach 
can benefit researchers to understand and visualize this kind of systems better.
In this paper a human-centered software framework was proposed, and was validated
through the implementaion and refinement of three C-IEC applications.
This framework enabled the implementation of a gamification technique 
to improve engagement in a case study which provides a common arena where users are aware of the
activities of other users in the social vicinity. Following a hybrid data model approach
gives developers and project owners options when innovating with other means
of interaction or new applications.

% More conclusions and some way of relating the three case studies
% would be something that is missing and should definitely go here - JJ

@@

Another line of work would be to study the possible negative effects of using  
gamification techniques to improve engagement, like cheating or
literally {\em gaming} the system to defeat competition. We already
found some hints of this behavior at the beginning of the release of
this system, but more subtle effect could be taking place. 
Finally, the refinement of the proposed Human-Centered framework will need
more case studies and further multi-disciplinary research.

\begin{acks}
  Reserved\\
  Space\\
  for acks\\
